Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-13 arxiv/experiments.tex
formatting

\section{Numerical Results}\label{sec_exp}

%We validate our  algorithmic insights and then our theory.
%In Section \ref{sec_exp_res}, we first show that single-task learning results can help predict positive or negative transfer.
%the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
%Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
%In Section \ref{sec_exp_ab}, we validate our theoretical results.
%We further show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings. The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
	\label{fig_same_cov}
\end{figure}

\subsection{Simulation Studies}\label{sec_simulation}

@@

\paragraph{Sample efficiency.}
First, we study the setting of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task   from $400$ to $2000$.
In all the parameter settings, our results estimate the empirical losses accurately.
We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, for $d = 0.2$, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires fewer samples per-task than STL. %\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at. For example, at the cross point, this ratio is 1. }

\paragraph{Sample ratio.}
Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
Again, our estimates are reasonably accurate compared to the empirical losses.
We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
The task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is $1$. We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increases when the sample ratio is above certain level.
On the other hand, when $d^2 = 0.045$, task two's prediction loss decreases monotonically.
Our work explains this trend as discussed below Corollary \ref{cor_MTL_loss}. \HZ{check}

\iffalse
We observe that as we increase the sample ratio, task two's prediction loss decreases initially but increases above the initial loss level.
Our work explains this trend since the task-specific variance $d^2 = 0.08$ is higher than task two's prediction loss, which is $\sigma^2 = 0.3^2$ times $p / (n_2 - p)$.
%We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
\fi

\paragraph{Covariate shift.}
Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}. 
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means more covariate shift.
Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
The noise variance $\sigma^2$ is $1/4$.
%Covariate shift: We set $\kappa = 1$ and $d = 0$.
%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).

@@

%\begin{table}
%	\begin{center}
%		\begin{tabular}{c c c c c}
%			\toprule
%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
%			\midrule
%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
			% {\bf CNN}  & 76\% & - & 32\% & -\\
%			\bottomrule
%		\end{tabular}
%	\end{center}
%	\caption{Taskonomy experiment.}
%	\label{tab:taskonomy}
%\end{table}

\begin{figure}[!t]
%		\begin{subfigure}[b]{0.32\textwidth}
%		\centering
%		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
%		\caption{Sample efficiency}
%		\label{fig_model_shift}
%	\end{subfigure}\hfill
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_several_d.eps}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
		\caption{Example \ref{ex_covshift}}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in Section \ref{sec_diff} for two tasks:
	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
	In Figure \ref{fig_size}, we discover several interesting phenomena by fixing task two's sample size and increasing task one's sample size.
	Depending on how large $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing when there is no bias.
	Having covariate shift increases task two's prediction loss when task two's sample size is larger than task one. Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
	\label{fig_model_shift_phasetrans}
\end{figure}

\subsection{Further Studies on Text Classification Tasks}\label{sec_text}

Our results and their implications are all in the high-dimensional linear regression setting.
How well do they extend to other scenarios?
In this section, we conduct further studies on six text classification datasets, for predicting whether a sentence has a positive or a negative sentiment.
Our datasets include a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
%The question is to predict positive or negative sentiment expressed in the text.
Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings. For LSTM, we add a shared feature representation layer on top of word embeddings.}

%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.
%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
%There are 14 diseases (tasks) for every image that we would like to predict.
%We use densenet121 as the shared module \cite{huang2017densely}.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
%We evaluate three model choices.
%\textit{Predicting transfer effect via STL results.}
%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
%A common challenge in the study of MTL is that the results can be hard to understand.
%It is difficult to predict when MTL performs well without running extensive trials.
%Our insight is that we can use STL results to help understand MTL results.
%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
%The results show that STL results are indicative of MTL results.

\paragraph{Sample size ratio.}
In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
We fix task one's sample size at $1000$ and increase task two's sample size from $100$ to $3000$.
These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops:
%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
\begin{itemize}
	\item We divide the source task data into $S$ batches.
	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
\end{itemize}
For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate until reaching the optimal sample ratio.
The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.

%\begin{algorithm}[!t]
%	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
%	\label{alg_inc_train}
%	\begin{algorithmic}[1]
%		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
%		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
%		\Output The trained modules $B, W_2$ optimized for task $2$.
%		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
%		\For{$i = 1,\dots, S$}
%			\For{$j = 1,\dots, T$}
%				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
%			\EndFor
%			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
%				\State \textbf{break}
%			\EndIf
%		\EndFor
%	\end{algorithmic}
%\end{algorithm}

%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
%\squishlist
%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
%TREC is less similar to MR because the task is about question types.
%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
We evaluate the progressive training procedure on the six text classification datasets.
First, we conduct multi-task training over all $15$ pairs from the six datasets.
We find that adding task one's samples progressive requires only $45\%$ of the computational cost to achieve the same test accuracy for task two than standard round-robin training schedules.
%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
%\textbf{Improving transfer learning training efficiency.}
%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
Second, we conduct multi-task training on all six datasets.
We find that adding samples progressively from all datasets requires less than $35\%$ of the computational cost to achieve the same test accuracy averaged over the six datasets than standard round-robin training schedules.
%As a further validation, excluding TREC, we observe similar comparative results.
%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

\begin{figure}%[!t]
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
		\caption{HPS vs. STL}
		\label{fig_ab_data}
	\end{subfigure}\hfill
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
		\caption{HPS vs. covariance alignment}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}:
	In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
	\label{fig_text}
%	\begin{minipage}[t]{0.4\textwidth}
%		\centering
%		\vspace{0pt}
%		\begin{tabular}{c c c}
%		\toprule
		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
		% Sentiment\\ analysis\end{center}\end{minipage}} \\
%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
		% \cmidrule(lr){2-3}
%		& all tasks & w/o TREC \\
%		\midrule
%		{\bf MLP}  & 31\% & 29\% \\
%		{\bf LSTM} & 35\% & 34\% \\
%		{\bf CNN}  & 30\% & 28\% \\
%		\bottomrule
%		\end{tabular}
%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
%		\label{tab:taskonomy}
%	\end{minipage}
\end{figure}

%	\begin{subfigure}[b]{0.33\textwidth}
%		\centering
%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
%		\caption{Task similarity}
%		\label{fig_ab_sim}
%	\end{subfigure}%
%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
%	(c)
%	Note: (S) denotes the source task and (T) denotes the target task.}

%\begin{minipage}[t]{.58\textwidth}
%	\vspace{-0.1in}
%	\centering
%  \begin{tabular}{c c c c c}
%	\toprule
%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
%		& Precision &  Recall & Precision &  Recall \\
%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
%	\bottomrule
%	\end{tabular}
%	\vspace{0.1in}
%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
%	\label{tab:mtl_better_than_stl}
%\end{minipage}%
%\quad

\paragraph{Covariate shift.}
Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
This highlights the need for correcting covariate shifts when the sample ratio rises.
To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, designed to correct covariate shifts.
The idea is to add an alignment module between the input and the shared module $B$.
This module is then trained together with $B$ and the output layers. We refer to \citet{WZR20} for more details about the procedure and the implementation.
%We validate our insight on this procedure in the experiments.
%We implement the covariance alignment procedure following \cite{WZR20}.

We conduct multi-task training on all $15$ task pairs from the six datasets.
In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
To get a robust comparison, we average the improvements over the 15 task pairs.
The result shows that as the sample ratio increases, performing covariance alignment provides more significant gains over HPS.
We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.

%\begin{figure}[!t]
%	\centering
%	\begin{subfigure}[b]{0.5\textwidth}
%		\centering
%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
%		\caption{Averaged over all 16 task pairs}
%		\label{fig_ab_cov}
%	\end{subfigure}\hfill
%	\begin{subfigure}[b]{0.5\textwidth}
%		\centering
%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
%		\caption{An example task pair}
%		\label{fig_cov_a}
%	\end{subfigure}
%	\caption{ (TREC and CR)}
%\end{figure}

%\textbf{Further results of the covariance alignment procedure.}
%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
%We leave this question for future work.
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

%\begin{figure}[!h]
%	\centering
%	\begin{subfigure}[b]{0.48\textwidth}
%		\centering
%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
%		\caption{Task pair TREC and CR}
%		\label{fig_cov_a}
%	\end{subfigure}\hfill
%		\begin{subfigure}[b]{0.48\textwidth}
%		\centering
%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
%		\caption{Task pair MR and SST}
%			\label{fig_cov_b}
%	\end{subfigure}
%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
%	\label{fig_covariate_app}
%\end{figure}

>>>>

\section{Simulation Studies}\label{sec_simulation}

@@

\textbf{Sample efficiency.}
First, we study the setting of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task   from $400$ to $2000$.
In all the parameter settings, our results estimate the empirical losses accurately.
We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, for $d = 0.2$, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires fewer samples per-task than STL. %\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at. For example, at the cross point, this ratio is 1. }

\textbf{Sample ratio.}
Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
Again, our estimates are reasonably accurate compared to the empirical losses.
We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
The task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is $1$. We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increases when the sample ratio is above certain level.
On the other hand, when $d^2 = 0.045$, task two's prediction loss decreases monotonically.
Our work explains this trend as discussed below Corollary \ref{cor_MTL_loss}. \HZ{check}

\textbf{Covariate shift.}
Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}. 
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means more covariate shift.
Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
The noise variance $\sigma^2$ is $1/4$.
%Covariate shift: We set $\kappa = 1$ and $d = 0$.
%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).

@@

%\begin{table}
%	\begin{center}
%		\begin{tabular}{c c c c c}
%			\toprule
%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
%			\midrule
%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
			% {\bf CNN}  & 76\% & - & 32\% & -\\
%			\bottomrule
%		\end{tabular}
%	\end{center}
%	\caption{Taskonomy experiment.}
%	\label{tab:taskonomy}
%\end{table}
%\begin{figure}[!t]
%	\centering
%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings. The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
%	\label{fig_same_cov}
%\end{figure}
